Create Figures and Tables

### 2023-09-02 Codes/2_figures_tables.rmd
minor fixes in yield intensive figures

g_ir_yield_both <-
  plot_yield_data %>%
  dplyr::mutate(g_yield = list(
    ggplot(plot_data) +
      geom_line(aes(
        y = y_hat,
        x = balance,
        color = factor(sat_cat_text)
      )) +
      scale_x_continuous(
        name = "Water Deficit (mm)",
        breaks = (-2:11) * 100
      ) +
      scale_y_continuous(
        name = "Yield (tonne/ha)",
        breaks = 0:(ceiling(max(plot_data$y_hat)) + 0.5),
        limits = c(NA, (ceiling(max(plot_data$y_hat)) + 0.5))
      ) +
      scale_color_discrete(
        name = "Aquifer Thickness",
        guide = guide_legend(
          title.position = "top",
          nrow = 2
        )
      ) +
      scale_fill_discrete(guide = "none") +
      theme_fig +
      coord_cartesian(xlim = c(-200, 1150)) +
      theme(
        legend.position = "bottom",
        plot.margin = margin(0, 0, 0, 0, "cm"),
        plot.title = element_blank()
      )
  ))

@@

g_yield_response <-
  cowplot::plot_grid(
    g_wd_corn, g_ir_yield_corn, g_wd_soy, g_ir_yield_soy,
    ncol = 1,
    align = "v",
    rel_heights = c(0.18 / 2, 0.69 / 2, 0.18 / 2, 0.95 / 2)
  )

>>>>

g_ir_yield_both <-
  plot_yield_data %>%
  dplyr::mutate(g_yield = list(
    ggplot(plot_data) +
      geom_line(aes(
        y = y_hat,
        x = balance,
        color = factor(sat_cat_text)
      )) +
      scale_x_continuous(
        name = "Water Deficit (mm)",
        breaks = (-2:11) * 100
      ) +
      scale_y_continuous(
        name = "Yield (tonne/ha)",
        breaks = 0:(ceiling(max(plot_data$y_hat)) + 0.5),
        limits = c(NA, (ceiling(max(plot_data$y_hat)) + 0.5))
      ) +
      scale_color_discrete(
        name = "Aquifer Thickness",
        guide = guide_legend(
          title.position = "top",
          nrow = 2
        )
      ) +
      scale_fill_discrete(guide = "none") +
      theme_fig +
      coord_cartesian(xlim = c(-200, 1150)) +
      theme(
        legend.position = "bottom",
        plot.margin = margin(0, 0, 0.0, 0, "cm"),
        plot.title = element_blank()
      )
  ))

@@

g_yield_response <-
  cowplot::plot_grid(
    g_wd_corn, 
    g_ir_yield_corn + theme(plot.margin = margin(0, 0, 0.2, 0, "cm")), g_wd_soy, 
    g_ir_yield_soy,
    ncol = 1,
    align = "v",
    rel_heights = c(0.18 / 2, 0.69 / 2, 0.18 / 2, 0.95 / 2)
  )
